ms_figures

### 2018-02-19 man/ms_2_results.Rmd
update results

The analysis of greenness time trends showed that 78.9 % of the pixels of *Quercus pyrenaica* forests experienced an EVI positive trend for the 2000-2016 period, of which 31.67 % were significant trends. The strongest trends were observed in southwestern populations (Figure S2), in which the Cañar site are included Vegetation greenness of *Q. pyrenaica* forests were lower during both the 2005 and 2012 years than the greenness observed for the reference period (Figure 2a). The lowest values for EVI standardized anomalies were recorded in 2005 being singnificantly lower (-2.285 ± 0.029) than those in 2012 (-0.418 ± 0.029) (LSMEANS, t.ratio = -45.358; p_value < 0.0001), particularly for northern populations (Figure 2b). Reduction in annual EVI mean was considerably higher in northern populations than in southern ones during the 2005 drought (Figure 2b).

According to the standardized anomalies, *Q. pyrenaica* forests suffered a "browning episode" during 2005 drought event (99.36 % and 79.37 % of the pixels for northern and southern populations respectively), yet no changes in greenness were observed in response to the 2012 drought (Figure S3).

@@

*Q. pyrenaica* forest showed significantly lower resistance (*Rt*) to the 2005 drought event than to that in 2012 (Table 3; Figure 3a). The 2005 drought reduced the greenness of oaks to a 85.8 % respect the reference period while the 2012 reduced it 94.3 % (Table S1). Southern populations showed significantly higher values of resistance to drought than northern ones (Table 3), except for 2012 where non-significant differences were recorded (Table S1. Figures 3a, 4a).

@@

The oak forests recovered (*Rc*) their greenness significantly more rapidly after the 2005 drought than after 2012 (Tables 3, S1). In the 3-year period after the 2005 drought, greenness achieved was 112 % (Rc = 1.12) and after 2012 was 105.7 % (Rc = 1.057) (Table S1). A similar recovery after the 2005 and 2012 drought event was observed for southern populations (p = 0.2453; Figure 4a), whilst the northern populations showed a significantly greater recovery after the 2005 drought than after the 2012 drought (Figure 4a).

@@

Resilience (*Rs*) was significantly higher for the 2012 drought event than for 2005 (Tables 3, S1), although both values were close to 1 indicating that greenness level was rather similar after each disturbance event (Table S1). The southern populations showed higher resilience values than the northern ones, although they were not significantly different for 2005 drought (p = 0.036; Figures 3a, 4a).

@@

Likely as a consequence of their different management origin (i.e. land-use legacy), the trees of the southern population were older than northern ones, particularly for the high elevation site (Ca-High) which had bigger and taller trees than the other sites (Tables 1, 2). The competition index was similar among sites but plot basal area was greatest in Ca-High (Table 1). Yet the basal area increment (BAI) growth in the highest plot in altitude (Ca-High) was the greatest  (Figure 5). Trees from this location showed in addition a positive growth trend since the late 1970s. This positive trend was not found in any of the other two locations and the two altitudes sampled in the Southern populations showed differences in growth, being more similar Ca_Low with growth in the Northern population (SJ) than with Ca_High (Figure 5). 
`VAS POR AQUI CARPINTO (BREAK)`

>>>>

The analysis of greenness time trends showed that 78.9 % of the pixels of *Quercus pyrenaica* forests experienced an EVI positive trend for the 2000-2016 period, of which 31.67 % were significant trends. The lowest values for EVI standardized anomalies were recorded in 2005, being singnificantly lower (-2.285 ± 0.029) than those in 2012 (-0.418 ± 0.029) (LSMEANS, t.ratio = -45.358; p_value < 0.0001), particularly for northern populations (Figure 2). According to the standardized anomalies, *Q. pyrenaica* forests suffered a "browning episode" during 2005 drought event (99.36 % and 79.37 % of the pixels for northern and southern populations respectively), yet no changes in greenness were observed in response to the 2012 drought (Figure S2).

```{r echo=FALSE, results='asis', eval=show_text}
cat("
The analysis of greenness time trends showed that 78.9 % of the pixels of *Quercus pyrenaica* forests experienced an EVI positive trend for the 2000-2016 period, of which 31.67 % were significant trends. The strongest trends were observed in southwestern populations (Figure S2), in which the Cañar site are included Vegetation greenness of *Q. pyrenaica* forests were lower during both the 2005 and 2012 years than the greenness observed for the reference period (Figure 2a). The lowest values for EVI standardized anomalies were recorded in 2005 being singnificantly lower (-2.285 ± 0.029) than those in 2012 (-0.418 ± 0.029) (LSMEANS, t.ratio = -45.358; p_value < 0.0001), particularly for northern populations (Figure 2b). Reduction in annual EVI mean was considerably higher in northern populations than in southern ones during the 2005 drought (Figure 2b).

According to the standardized anomalies, *Q. pyrenaica* forests suffered a browning episode during 2005 drought event (99.36 % and 79.37 % of the pixels for northern and southern populations respectively), yet no changes in greenness were observed in response to the 2012 drought (Figure S3). 
")
```

@@

*Q. pyrenaica* forest showed significantly lower resistance (*Rt*) to the 2005 drought event than to that in 2012 (Table 3; Figure 3a). Southern populations showed significantly higher values of resistance to drought than northern ones (Table 3), except for 2012 where non-significant differences were recorded (Table S1; Figures 3a).

@@

In the 3-year period after the 2005 drought, greenness achieved was 112 % (Rc = 1.12) and after 2012 was 105.7 % (Rc = 1.057) (Table S1). A similar recovery after the 2005 and 2012 drought event was observed for southern populations (p = 0.2453; Figure 4a), whilst the northern populations showed a significantly greater recovery after the 2005 drought than after the 2012 drought (Figure 4a).

@@

Resilience (*Rs*) was significantly higher for the 2012 drought event than for 2005 (Tables S1, 3), although both values were close to 1 indicating that greenness level was rather similar after each disturbance event (Table S1). The southern populations showed higher resilience values than the northern ones, although they were not significantly different for 2005 drought (p = 0.036; Figures 3a, 4a).

@@

Likely as a consequence of their different management origin (*i.e.* land-use legacy), the trees of the southern population were older than northern ones, particularly for the high elevation site (Ca-High) which had bigger and taller trees than the other sites (Tables 1, 2). The competition index was similar among sites but plot basal area was greatest in Ca-High (Table 1). Yet the basal area increment (BAI) growth in the highest plot in altitude (Ca-High) was the greatest (Figure 5). Trees from this location showed in addition a positive growth trend since the late 1970s. This positive trend was not found in any of the other two locations and the two altitudes sampled in the Southern populations showed differences in growth, being more similar Ca_Low with growth in the northern population (SJ) than with Ca_High (Figure 5). 
`VAS POR AQUI CARPINTO (BREAK)`

### 2018-02-19 man/ms_figures.Rmd
update results

## Figure 2. Plot combinado con EVI profile (a) y anomalías (b)
")
```

@@

```{r}
iv <- read.csv(here("data/evi", "iv_composite.csv"), header = TRUE, sep = ',')

@@

```{r, fig.height=7}
a_profile_compara <- profile_compara + labs(title = "a")
b_plot_sa_clu <- plot_sa_clu + labs(title = "b")
a_profile_compara + b_plot_sa_clu + plot_layout(ncol=1)
```

**Figure 2.** Comparison of EVI profile for the reference period (*gray*) and during the 2005 (*green*) and 2012 (*blue*) drought events (a) (mean of all analyzed pixels). EVI standardized anomaly ($EVI~sa$) during the period 2000-2016 for northern and southern populations (b). Error bars show standard error.

@@

>>>>

## Figure 2. Plot de anomalias
- [X] Solamente Anomalias estandarizadas

## Figure 3. 
")
```

@@

```{r, eval=FALSE}
iv <- read.csv(here("data/evi", "iv_composite.csv"), header = TRUE, sep = ',')

@@

```{r, fig.height=7, eval=FALSE}
a_profile_compara <- profile_compara + labs(title = "a")
b_plot_sa_clu <- plot_sa_clu + labs(title = "b")
a_profile_compara + b_plot_sa_clu + plot_layout(ncol=1)
```

```{r, fig.height=7}
plot_sa_clu 
```

**Figure 2.** EVI standardized anomaly ($EVI~sa$) during the period 2000-2016 for northern and southern populations. Error bars show standard error.

@@

```{r}

resilience_metrics <- c("0_rt" = "Resistance", "1_rc" = "Recovery", "2_rs" = "Resilience")
variables <- c("0_EVI"="EVI", "1_BAI"="BAI")
# width
w <- .6
pos <- position_dodge(width=w)

line_lwd <- .8

aux <- mhuber_filter %>% mutate(vari = '0_EVI')
aux2 <- mhuberbai_filter %>% mutate(vari = '1_BAI')
m <- bind_rows(aux2, aux)

m %>% 
  ggplot(aes(x = disturb_year, y = M.Huber, 
                   color = site, group = site, 
                   fill = site,
                   ymin = lower.ci, ymax = upper.ci)) + 
  geom_bar(stat = "identity", position="dodge", width=w) +
  geom_errorbar(width=.2, position = pos) + 
  facet_grid(var_sorted~vari, labeller = labeller(
    var_sorted = resilience_metrics, 
    vari = variables), 
    scales = "free_y") + theme_bw() + 
  theme_bw() + 
  theme(
    panel.grid.minor = element_blank(),
    strip.background = element_rect(
      colour = "black",
      fill = "white"),
    strip.text = element_text(face="bold", size = 14),
    plot.title = element_text(hjust = -0.05, size = 16, margin = margin(t=-5, b=1)))+  
  ylab("Response value")+
  xlab('Drought event') + 
  geom_text(aes(label=Letter, y = (M.Huber + .05*lower.ci)), position=pos, vjust=-2) + 
  scale_color_manual(values=c('gray', "#104E8B", 'gray', "#1E90FF", "#104E8B")) +
  scale_fill_manual(values=c('gray', "#104E8B", 'gray', "#1E90FF", "#104E8B"))
